Results

### 2018-07-09 02_analysis.Rmd
Better patchwork annotations + facet titles

```{r plot-all-amount-medians, fig.width=8, fig.height=6}
((plot_amount_c + 
   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_amount_ci) | plot_amount_cif

((plot_amount_c / plot_amount_ci) | 
    plot_amount_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
((plot_diffs_c + 
   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_ci) | plot_diffs_cif

((plot_diffs_c / plot_diffs_ci) | 
    plot_diffs_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-likely-medians, fig.width=8, fig.height=6}
((plot_likely_c + 
   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_likely_ci) | plot_likely_cif

((plot_likely_c / plot_likely_ci) | 
    plot_likely_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
((plot_diffs_likely_c + 
   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_likely_ci) | plot_diffs_likely_cif

((plot_diffs_likely_c / plot_diffs_likely_ci) | 
    plot_diffs_likely_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

>>>>

```{r plot-all-amount-medians, fig.width=8, fig.height=6}
plot_amount_all <- 
  (plot_amount_c / plot_amount_ci) | 
  plot_amount_cif

plot_amount_all +
  plot_annotation(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
                  subtitle = "90% credible intervals shown around each point",
                  tag_levels = "A", theme = theme_ngos())

(plot_amount_all + 
    plot_annotation(caption = "90% credible intervals shown around each point",
                    tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
plot_diffs_all <- 
  (plot_diffs_c / plot_diffs_ci) | 
  plot_diffs_cif

plot_diffs_all +
  plot_annotation(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())

(plot_diffs_all +
  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-likely-medians, fig.width=8, fig.height=6}
plot_likely_all <- 
  (plot_likely_c / plot_likely_ci) | 
  plot_likely_cif

plot_likely_all +
  plot_annotation(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
                  subtitle = "90% credible intervals shown around each point",
                  tag_levels = "A", theme = theme_ngos())

(plot_likely_all +
  plot_annotation(caption = "90% credible intervals shown around each point",
                  tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
plot_diffs_likely_all <- 
  (plot_diffs_likely_c / plot_diffs_likely_ci) | 
  plot_diffs_likely_cif

plot_diffs_likely_all +
  plot_annotation(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())

(plot_diffs_likely_all +
  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```
